Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method (EBASE)

### 2023-10-19 manu-draft.qmd
fix apadef plot figure caption
minor text edit

The synthetic time series was used as input to EBASE to predict metabolic parameters with the default prior distributions above. Two optimization periods of 7 and 30 days were evaluated. This analysis provided a demonstration that the default priors are not entirely unreasonable based on the ability to reproduce the known parameters in the synthetic time series [@fig-defplo]. Overall, EBASE produced reasonable results for $a$ and $R$, with higher accuracy using the 30 day optimization period (Figure [-@fig-defplo]b) compared to the 7 day optimization period (Figure [-@fig-defplo]a).  However, the model was unable to return the $b$ parameter with acceptable accuracy, suggesting the data were insufficient to constrain this parameter.  Further, many of the 95% credible intervals from the posterior distributions of each parameter did not overlap the known values from the synthetic time series.  Estimates for each optimization period may be inaccurate despite overall similarities comparing all estimates to the known values for the whole year.

@@

![Comparison of EBASE results with default prior distributions to a synthetic time series created with known model parameters ($a$, $R$, and $b$).  Results are compared for EBASE parameters estimated with a (a) 7 day and (b) 30 day optimization period. 95% credible intervals from the posterior distributions of the parameter estimates from EBASE are also shown. The results are averaged at the time step of the model optimization period.](figs/defplo.png){#fig-defplo}

>>>>

The synthetic time series was used as input to EBASE to predict metabolic parameters with the default prior distributions above. Two optimization periods of 7 and 30 days were evaluated. This analysis provided a demonstration that the default priors are not entirely unreasonable based on the ability to reproduce the known parameters in the synthetic time series ([@fig-defplo]). Overall, EBASE produced reasonable results for $a$ and $R$, with higher accuracy using the 30 day optimization period (Figure [-@fig-defplo]b) compared to the 7 day optimization period (Figure [-@fig-defplo]a).  However, the model was unable to return the $b$ parameter with acceptable accuracy, suggesting the data were insufficient to constrain this parameter.  Further, many of the 95% credible intervals from the posterior distributions of each parameter did not overlap the known values from the synthetic time series.  Estimates for each optimization period may be inaccurate despite overall similarities comparing all estimates to the known values for the whole year.

@@

![Comparison of EBASE results using default prior distributions to a synthetic time series created with known model parameters ($a$, $R$, and $b$).  Results are compared for EBASE parameters estimated with a (a) 7 day and (b) 30 day optimization period. 95% credible intervals from the posterior distributions of the parameter estimates from EBASE are also shown. The results are averaged at the time step of the model optimization period.](figs/defplo.png){#fig-defplo}
